\usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{STEM Fellowship Big Data Challenge 2020} \\ [10pt] \huge Deep learning transcriptomic model for prediction of pan-drug chemotherapeutic sensitivity \\

### 2020-06-30 manuscript/manuscript.tex
fixed J formula

    \caption{(\textbf{A}) ROC curves for 1, 5, 10, and 15 hidden layers neural network models. Each model was subject to 5-fold stratified cross-validation on the training set, and the mean ROC curve for the testing set across all trials was plotted. (\textbf{B}) Confusion matrices for the 1, 5, 10, and 15 hidden layer neural network models on the testing set. The threshold for classification determiend using Youden's index (thresholds were 0.17, 0.97, 0.49, and 0.45 for neural networks with 1, 5, 10, and 15 hidden layers respectively). The models classify cell line microarray datasets into chemotherapy response cohorts.}
    \label{fig:nnet}
\end{figure*}

@@

Following grid search and cross-validation, we evaluated the performance of our model on the testing data. Youden's index from the ROC curves corresponding to each neural network was used to determine the optimal threshold to classify cell lines into chemotherapeutic response groups. The formula for Youden's index is defined as $$J \doteq \text{sensitivity} - \text{specificity} - 1$$ All indices were obtained from the ROC curves by an iterative search for the maximum $J$. That is, $$J = \text{argmax(TPR} - \text{FPR)}$$ where TPR and FPR are arrays containing the true positive and false positive fate corresponding to each point on the ROC curve. The threshold corresponding to $J$ was used to classify cell lines.

@@

% neural net evaluation figure
\begin{figure*}[!ht]
	\centering
	\begin{subfigure}[t]{\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/confusion_matrix/cm_combined.png}
	\end{subfigure}

	\begin{subfigure}[t]{\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/roc/cv_roc.png}
	\end{subfigure}

	\caption{(\textbf{A}) Confusion matrices for the 1, 5, 10, and 15 hidden layer neural network models on the validation set. The models classify cell line microarray datasets into chemotherapy response cohorts. (\textbf{B}) ROC curves for 1, 5, 10, and 15 hidden layers neural network models with confidence bands of $\pm 1$ standard error of the mean (sem). Each model was subject to 5-fold stratified cross-validation on the training set, and the mean ROC curve for the validation set across all trials was plotted.}
	\label{fig:nnet_train}
\end{figure*}

@@

\subsection{Tables}
\begin{table*}[h]
    \caption{Grid search parameters to optimize all implemented neural network architectures (1, 5, 10, and 15 hidden layers). Each grid search underwent 3-fold cross-validation on the training data. Optimal parameters: 25 epochs, batch size of 16, 100 neurons, $\lambda=10^{-3}$, Adam as optimizer, normal kernel initializer.}
    \centering
    \label{tab:params}
    \begin{tabular}{l l l l l l}
        \toprule
        Epochs & Batches & Neurons & $\lambda$ (L2 reg) & Optimizer & Kernel initializer \\
        \midrule
        25 & 16 & 50 & 1e-4 & Sgd & Normal \\
        50 & 32 & 100 & 1e-3 & Adagrad & Uniform \\
        75 & 64 & 150 & 1e-2 & Adam & Glorot uniform \\
        \bottomrule
    \end{tabular}
\end{table*}

>>>>

    \caption{(\textbf{A}) ROC curves for 1, 5, 10, and 15 hidden layers neural network models. Each model was subject to 5-fold stratified cross-validation on the training set, and the mean ROC curve for the testing set across all trials was plotted. (\textbf{B}) Confusion matrices for the 1, 5, 10, and 15 hidden layer neural network models on the testing set. The threshold for classification determined using Youden's index (thresholds were 0.17, 0.97, 0.49, and 0.45 for neural networks with 1, 5, 10, and 15 hidden layers respectively). The models classify cell line microarray datasets into chemotherapy response cohorts.}
    \label{fig:nnet}
\end{figure*}

@@

Following grid search and cross-validation, we evaluated the performance of our model on the testing data. Youden's index from the ROC curves corresponding to each neural network was used to determine the optimal threshold to classify cell lines into chemotherapeutic response groups. The formula for Youden's index is defined as $$J \doteq \text{sensitivity} + \text{specificity} - 1$$ All indices were obtained from the ROC curves by an iterative search for the maximum $J$. That is, $$J = \text{argmax(TPR} - \text{FPR)}$$ where TPR and FPR ($\text{FPR} = 1 - \text{specificity}$) are arrays containing the true positive and false positive fate corresponding to each point on the ROC curve. The threshold corresponding to $J$ was used to classify cell lines.

@@

% neural net evaluation figure
\begin{figure*}[!ht]
	\centering
		\begin{subfigure}[t]{\textwidth}
			\centering
			\includegraphics[width=\textwidth]{Figures/roc/cv_roc.png}
		\end{subfigure}

	\begin{subfigure}[t]{\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/confusion_matrix/cm_combined.png}
	\end{subfigure}

	\caption{(\textbf{A}) ROC curves for 1, 5, 10, and 15 hidden layers neural network models with confidence bands of $\pm 1$ standard error of the mean (sem). Each model was subject to 5-fold stratified cross-validation on the training set, and the mean ROC curve for the validation set across all trials was plotted.  (\textbf{B}) Confusion matrices for the 1, 5, 10, and 15 hidden layer neural network models on the validation set. The models classify cell line microarray datasets into chemotherapy response cohorts. Threshold to classify cell lines into response cohorts is 0.5.}
	\label{fig:nnet_train}
\end{figure*}

@@

\subsection{Tables}
\begin{table*}[h]
    \caption{Grid search parameters to optimize all implemented neural network architectures (1, 5, 10, and 15 hidden layers). Each grid search underwent 3-fold cross-validation on the training data. Optimal parameters: 50 epochs, batch size of 32, 50 neurons, $\lambda=10^{-3}$, Adam as optimizer, normal kernel initializer.}
    \centering
    \label{tab:params}
    \begin{tabular}{l l l l l l}
        \toprule
        Epochs & Batches & Neurons & $\lambda$ (L2 reg) & Optimizer & Kernel initializer \\
        \midrule
        25 & 16 & 50 & 1e-4 & Sgd & Normal \\
        50 & 32 & 100 & 1e-3 & Adagrad & Uniform \\
        75 & 64 & 150 & 1e-2 & Adam & Glorot uniform \\
        \bottomrule
    \end{tabular}
\end{table*}
